Dish: Distribution-oblivious Shell Scripting

### 2020-02-23 osdi/draft.tex
Notes on ICFP/OSDI

* 
Extends beyond linear pipelines to full programs 
that comply with the POSIX shell specification; while \sys does not optimize
everything---it certainly cannot---, it does

>>>>

* new evaluation case
* split / micro-batching optimizations
* rewrite paper
* DSL

Extends beyond linear pipelines to full programs 
that comply with the POSIX shell specification; while \sys does not optimize
everything---it certainly cannot---, it does
